---
title: "6. R API Training - Continuous Model Training [Solution]"
author: "Thodoris Petropoulos and Chester Ismay<br>Contributors: Rajiv Shah"
output: github_document
---

This is the 6th exercise to complete in order to finish your `R API Training for DataRobot` course! This exercise teaches you how to deploy a trained model, make predictions (**Warning**: Multiple ways of getting predictions out of DataRobot), and monitor drift to replace a model.

Here are the actual sections of the notebook alongside time to complete: 

1. Connect to DataRobot. [3min]<br>
2. Retrieve the first project created in `Exercise 4 - Model Factory`. [5min]
3. Search for the `recommended for deployment` model and deploy it as a rest API. [20min]
4. Create a scoring procedure  using dataset (1) that will force data drift on that deployment. [25min]
5. Check data drift. Does it look like data is drifting?. [3min]
6. Create a new project using data (2). [5min]
7. Replace the previously deployed model with the new `recommended for deployment` model from the new project. [10min]

Each section will have specific instructions so do not worry if things are still blurry!

As always, consult:

- [API Documentation via CRAN Vignettes](https://CRAN.R-project.org/package=datarobot)
- [Samples](https://github.com/datarobot-community/examples-for-data-scientists)
- [Tutorials](https://github.com/datarobot-community/tutorials-for-data-scientists)

The last two links should provide you with the snippets you need to complete most of these exercises.

<b>Data</b>

(1) The dataset we will be using throughout these exercises is the well-known `readmissions dataset`. You can access it or directly download it through DataRobot's public S3 bucket [here](https://s3.amazonaws.com/datarobot_public_datasets/10k_diabetes.csv).

(2) This dataset will be used to retrain the model. It can be accessed [here](https://s3.amazonaws.com/datarobot_public_datasets/10k_diabetes_scoring.csv) through DataRobot's public S3 bucket.

### Import Packages
Import packages here as you start finding out what packages are needed. The DataRobot package is already included for your convenience.

```{r}
```


### 1. Connect to DataRobot. [3min]<br>

```{r}
```

### 2. Retrieve the first project created in `Exercise 5 - Model Factory` . [5min]

This should be the first project created during the exercise. Not one of the projects created using a sample of `admission_type_id`.

```{r eval=FALSE}
#Proposed Solution
project <- GetProject('YOUR_PROJECT_ID')
```


### 3. Search for the `recommended for deployment` model and deploy it as a rest API. [10min]

**Hint**: The recommended model can be found using the `GetModelRecommendation()` function. 

**Hint 2**: Use the `UpdateDeploymentDriftTrackingSettings()` function on the DataRobot Deployment object to enable data drift tracking.

```{r}
```

### 4. Create a scoring procedure using dataset (1) that will force data drift on that deployment.  [25min]

**Instructions**
1. Take the first 100 rows of dataset (1) and save them to a data frame
2. Score 5 times using these observations to force drift.
3. Use the deployment you created during `question 3`.

**Hint**: The only thing you will have to change for the code to work is change the filename variable to point to the csv file to be scored and create a for loop.

```{r}
```


```{r}
```

```{r}
```


### 5. Check data drift. Does it look like data is drifting?. [3min]

Check data drift from within the `Deployments` page in the UI for the Readmissions Deployment. Is data drift marked as red?

### 6. Create a new project using data (2). [5min]

Link to data: <https://s3.amazonaws.com/datarobot_public_datasets/10k_diabetes_scoring.csv>

```{r}
```

### 7. Replace the previously deployed model with the new `recommended for deployment` model from the new project. [10min]

**Hint**: You will have to provide a reason why you are replacing the model. Explore the `ModelReplacementReason` list for options.

```{r}
```

