---
title: "7. R API Training - Using a Database [Solution]"
author: "Thodoris Petropoulos and Chester Ismay<br>Contributors: Rajiv Shah"
output: github_documentx
---

This is the 7th exercise to complete in order to finish your R API Training for DataRobot course! This exercise teaches you how to use a database in order to read datasets to train models or dump your predictions in a table.

Here are the actual sections of the notebook alongside time to complete:

1. Connect to DataRobot. [3min]
2. Connect to the SQLite database provided. [5min]
3. Load the `readmissions` dataset that needs scoring. [10min]
4. Use one of the deployments generated earlier to score the dataset. [15min]
5. Writeback predictions in the database

As always, consult:

- [API Documentation via CRAN Vignettes](https://CRAN.R-project.org/package=datarobot)
[Samples](https://github.com/datarobot-community/examples-for-data-scientists) <br>
[Tutorials](https://github.com/datarobot-community/tutorials-for-data-scientists)

The last two links should provide you with the snippets you need to complete most of these exercises.

**Data**

The dataset used in the current exercise can be reached via `databases/test_database.db`

### Import Packages
Import packages here as you start finding out what packages are needed. The DataRobot package is already included for your convenience.

```{r}
```


### 1. Connect to DataRobot. [3min]<br>

```{r eval=FALSE}
```

```{r echo=FALSE}
```


#### 2. Connect to the SQLite database provided. [5min]

The SQLite database is under the folder `databases` with filename `test_database.db`. To create a connection, use the `sqlite3` package. It becomes apparent that while using R, it really does not matter where your data is, you could just invoke the appropriate packages and load your data.

```{r}
```

### 3. Load the readmissions dataset that needs scoring. [10min]
The readmissions dataset is saved within the `test_database`.

**Instructions** 
1. Query the first 100 observations.
2. Save them into a data frame that is outputted as a CSV.

```{r}
```


#### 4. Use one of the deployments generated earlier to score the dataset. [15min]
**Instructions**
1. Navigate to `Deployments` page within DataRobot.
2. Use the R code from the previous exercise to make a prediction with this deployment         
    - specifying `filename` in the call to the `main()` function as this CSV file we just created from the first 100 rows of the readmissions table and
    - updating the deployment ID with your value.
3. Score the dataset and save the results in a new data frame.

```{r}
```

```{r}
```

#### 5. Writeback predictions in the database

**Instructions**
1. Join the results table with the original data used to score
2. Save the results in a table called `prediction_results` within the `test_database_db`

**Hint**: Check out the {DBI} R package for ways to write tables to a database.

```{r}
```
