---
title: "5. R API Training - Model Factory [Solution]"
author: "Thodoris Petropoulos and Chester Ismay<br>Contributors: Rajiv Shah"
output: github_document
---

This is the 5th exercise to complete in order to finish your `R API Training for DataRobot` course! This exercise teaches you how to leverage DataRobot in order to create a model factory. That could help you increase model accuracy and shows you the true capabilities of an AutoML platform.

Here are the actual sections of the notebook alongside time to complete: 

1. Connect to DataRobot. [3min]<br>
2. Create a data frame/tibble with the `readmissions` dataset. [3min]
3. Create a DataRobot Project with the `readmissions` dataset explicitly using `quick` autopilot. [5min]
4. Split the dataset and run multiple DataRobot Projects based on the `admission_type_id` column explicitly using `quick` autopilot. [25min]
5. Check the validation scores of the best models for each one of the projects. What do you see? [15min]

Each section will have specific instructions so do not worry if things are still blurry!

As always, consult:

- [API Documentation via CRAN Vignettes](https://CRAN.R-project.org/package=datarobot)
- [Samples](https://github.com/datarobot-community/examples-for-data-scientists)
- [Tutorials](https://github.com/datarobot-community/tutorials-for-data-scientists)

The last two links should provide you with the snippets you need to complete most of these exercises.

<b>Data</b>

The dataset we will be using throughout these exercises is the well-known `readmissions dataset`. You can access it or directly download it through DataRobot's public S3 bucket [here](https://s3.amazonaws.com/datarobot_public_datasets/10k_diabetes.csv).

### Import Packages
Import packages here as you start finding out what packages are needed. The DataRobot package is already included for your convenience.

```{r}
# Proposed packages needed
library(dplyr)
library(purrr)
library(readr)
```


### 1. Connect to DataRobot. [3min]<br>

```{r}
# Possible solution
datarobot::ConnectToDataRobot(configPath = "../config.yaml")

# After connecting, load the datarobot package
library(datarobot)
```

### 2. Create a data frame/tibble with the `readmissions` dataset. [3min]

```{r}
# Proposed Solution

df <- read_csv("https://s3.amazonaws.com/datarobot_public_datasets/10k_diabetes.csv")
head(df)
```

### 3. Create a DataRobot Project with the `readmissions` dataset explicitly using `quick` autopilot. [5min]


**Instructions**:
1. Use the `StartProject()` function.
2. Set `readmitted` as the target.
3. Start the project using explicitly the `quick` autopilot in the `mode` variable.
4. Update the project to have a `worker_count` variable of -1.
5. Wait for (Quick) Autopilot to complete.

**HINT**: You should have already done something similar during the 1st exercise of this course.

```{r}
#Possible solution
project <- StartProject(
  dataSource = df, 
  projectName = "05_Model_Factory_01",
  target = "readmitted",
  mode = "quick"
)
UpdateProject(project, workerCount = -1)
```

### 4. Split the dataset and run multiple DataRobot Projects based on the `admission_type_id` column explicitly using `quick` autopilot. [25min]

**Hint**: Some `admission_type_id` values have less than 100 rows. That is the minimum requirement to start a DataRobot project. You should create an exception and just skip those admission types.

**Hint 2**: This will take a long time to execute. You can either execute for only a small part of the different `admission_type_id` values or just move on to the next exercise while this is executing.


```{r}
#Proposed Solution

less_than_100 <- df %>% 
  count(admission_type_id) %>% 
  filter(n <= 100) %>% 
  pull(admission_type_id)

modified_df <- df %>% 
  filter(!admission_type_id %in% less_than_100)

project_list <- modified_df %>%
  group_by(admission_type_id) %>%
  group_map(~ StartProject(
    dataSource = .x,
    projectName = paste0("Readmission_", .y$admission_type_id),
    target = "readmitted",
    mode = "quick"
  ))

walk(project_list, UpdateProject, workerCount = -1)
walk(project_list, WaitForAutopilot, verbosity = 0)
```



### 5. Check the validation scores of the best models for each one of the projects. What do you see? [15min]

- Based on `AUC` score

**Hint**: The `ListProjects()` function takes a `filter` parameter that you can
use to search for different phrases in the names of your projects. It returns
a `projectSummaryList` that can be further examined.

```{r}
#Proposed Solution

these_projects <- ListProjects(filter = list("projectName" = "Readmission_"))

#Get best model from original project which has been trained on all of the data.
ListModels(project)[[1]]$metrics$AUC$validation

#Get best model from each one of the projects trained on a subset of data based 
#on `admission_type_id`.
for (proj_id in these_projects$projectId) {
  top_model <- ListModels(project = proj_id)[[1]]
  print(paste0(top_model$projectName, ": ", top_model$metrics$AUC$validation))
}
```
